---
title: "p8105_hw3_hx2328"
author: "Hao Xu"
date: "10/20/2021"
output: github_document
---

```{r setup}
library(tidyverse)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

```{r}
library(p8105.datasets)
data("instacart")
```

`This dataset collects `r nrow(instacart)` observations, each row is a single product that customer buy using instacart. There are `r ncol(instacart)` variables. The key variable includes "add_to_cart_order" representing the order that customer adds the product to the cart; "reordered" representing if the customer has ordered it before; "order_dow" represenging the day of the week that costomer orders; and "aisle" representing the name of the aisle.

## How many aisles are there, and which aisles are the most items ordered from?

```{r}
aisle_count = 
  instacart %>% 
  group_by(aisle) %>% 
  summarise(n_obs = n())
head(aisle_count)
```

Here, we got the counts of each aisle, there are totally `r nrow(aisle_count)` different kinds of aisles. To get the most popular one, we could do following:

```{r}
aisle_count %>% 
  filter(n_obs == max(n_obs))
```

Therefore, we got that the most popular one is "fresh vegetables", and it has been ordered 150609 times.
