---
title: "p8105_hw3_hx2328"
author: "Hao Xu"
date: "10/20/2021"
output: github_document
---

```{r setup}
library(tidyverse)
library(patchwork)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Problem 1

```{r}
library(p8105.datasets)
data("instacart")
```

`This dataset collects `r nrow(instacart)` observations, each row is a single product that customer buy using instacart. There are `r ncol(instacart)` variables. The key variable includes "add_to_cart_order" representing the order that customer adds the product to the cart; "reordered" representing if the customer has ordered it before; "order_dow" represenging the day of the week that costomer orders; and "aisle" representing the name of the aisle.

## How many aisles are there, and which aisles are the most items ordered from?

```{r}
aisle_count = 
  instacart %>% 
  group_by(aisle) %>% 
  summarise(n_obs = n())
head(aisle_count)
```

Here, we got the counts of each aisle, there are totally `r nrow(aisle_count)` different kinds of aisles. To get the most popular one, we could do following:

```{r}
aisle_count %>% 
  filter(n_obs == max(n_obs))
```

Therefore, we got that the most popular one is "fresh vegetables", and it has been ordered 150609 times.

## Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.

First only get the aisles more than 10000, and arrange them from according to the number of items:

```{r}
aisle_count = 
  aisle_count %>% 
  filter(n_obs >= 10000) %>% 
  mutate(aisle = forcats::fct_reorder(aisle, n_obs))
```

Then get the scatter plot showing the numbers of items ordered in each aisle:

```{r}
aisle_count_plot = 
  aisle_count %>% 
  ggplot(aes(x = n_obs, y = aisle, color = aisle)) +
  geom_point() +
  theme(legend.position = "none") +
  labs(
    title = "number of aisle scatter plot",
    x = "Number of items ordered",
    y = "Aisle name",
    caption = "Data from the p8105.dataset package, only shows items greater than or equal to 10000"
  )
aisle_count_plot
```

## Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.

```{r}
selected_aisle_table = 
  instacart %>% 
  filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
    summarise(n_obs = n()) %>% 
  mutate(product_ranking = min_rank(desc(n_obs))) %>% 
  filter(product_ranking %in% c(1, 2, 3)) %>% 
  arrange(desc(n_obs)) %>% 
  knitr::kable()

selected_aisle_table
```

## Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).

```{r}
mean_hour_table = 
  instacart %>% 
  select(product_name, order_dow, order_hour_of_day) %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  group_by(product_name, order_dow) %>% 
  summarise(mean_order_hour_of_day = mean(order_hour_of_day)) %>% 
  pivot_wider(names_from = product_name,
              values_from = mean_order_hour_of_day) %>% 
  knitr::kable()
  
mean_hour_table
```


# Problem 2

```{r}
data("brfss_smart2010")
```

Firstly clean and tidy the data.

```{r}
brfss_smart2010 = 
  brfss_smart2010 %>% 
  janitor::clean_names() %>% 
  filter(topic == "Overall Health",
         response %in% c("Excellent", "Very good", "Good", "Fair", "Poor")) %>% 
  mutate(response = forcats::fct_relevel(response, c("Poor", "Fair", "Good", "Very good", "Excellent"))) %>% 
  rename(state = locationabbr,
         state_location = locationdesc)
```

## In 2002, which states were observed at 7 or more locations? What about in 2010?

For 2002:

```{r}
brfss_smart2010 %>% 
  filter(year == 2002) %>% 
  group_by(state, state_location) %>% 
  summarise(n_obs = n()) %>% 
  group_by(state) %>% 
  summarise(num_locations = n()) %>% 
  filter(num_locations >= 7) %>% 
  knitr::kable()
```

As a result, the states that were observed at 7 or more locations in 2002 are: CT, FL, MA, NC, NJ, PA.

For 2010:

```{r}
brfss_smart2010 %>% 
  filter(year == 2010) %>% 
  group_by(state, state_location) %>% 
  summarise(n_obs = n()) %>% 
  group_by(state) %>% 
  summarise(num_locations = n()) %>% 
  filter(num_locations >= 7) %>% 
  knitr::kable()
```

As a result, the states that were observed at 7 or more locations in 2010 are: CA, CO, FL, MA, MD, NC, NE, NJ, NY, OH, PA, SC, TX, WA.

## Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).


